A multiverse analysis of the associations between internet use and well-being

### 2023-11-13 ms.Rmd
Sample specs for synthetic data

# Environment options
DATA_PATH_GWP <- Sys.getenv(
  "DATA_PATH_GWP"
)
DATA_PATH_GWP_CLEAN <- "data-raw/gwp.rds"
DATA_PATH_SYN <- Sys.getenv(
  "DATA_PATH_SYN",
  unset = "data-synthetic/synthetic-data.rds"
)
MAX_CORES <- as.numeric(
  Sys.getenv(
    "MAX_CORES", 
    unset = parallel::detectCores(logical = FALSE)
  )
)

@@

specs <- expand_grid(
  distinct(dat, sex, age),
  y = ys,
  x = xs,
  covariate = cs,
  weights = c("No", "Yes")
) %>% 
  # Drop year from formula for GWB outcomes (only ~1 year)
  mutate(
    formula = if_else(
      str_starts(y, "gwb_"),
      str_glue("{y} ~ {x} + {covariate} + ({x} | country)"),
      str_glue("{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)"),
    )
  )
```

>>>>

# Environment options
DATA_PATH_GWP <- Sys.getenv(
  "DATA_PATH_GWP"
)
DATA_PATH_GWP_CLEAN <- "data-raw/gwp.rds"
DATA_PATH_SYN <- Sys.getenv(
  "DATA_PATH_SYN"
)
MAX_CORES <- as.numeric(
  Sys.getenv(
    "MAX_CORES", 
    unset = parallel::detectCores(logical = FALSE)
  )
)

@@

specs <- expand_grid(
  distinct(dat, sex, age),
  y = ys,
  x = xs,
  covariate = cs,
  weights = c("No", "Yes")
) %>% 
  # Drop year from formula for GWB outcomes (only ~1 year)
  mutate(
    formula = if_else(
      str_starts(y, "gwb_"),
      str_glue("{y} ~ {x} + {covariate} + ({x} | country)"),
      str_glue("{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)"),
    )
  )

# If only simulated data exists, sun small subset of specs
set.seed(9091090)
if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = MAX_CORES)
```
